What\,Agreement\,Hath\,Mars\,With\,Earth? \\ An Exploration of Urbit's IPC Interfaces

### 2024-03-11 mss.tex
Break title lines better.
Post PDF update

%%MANUSCRIPT
\title{What Agreement Hath Mars With Earth?  An Exploration of Urbit's IPC Interfaces}
\author{~\authorpatp \\ \affiliation}
\date{}

@@

@@

\begin{lstlisting}[
  float,
  style=listingcode,
  caption={Usage of \texttt{\%lick} cards.},
  label={lst:lick-cards}
]
++  init  [[%pass / %arvo %l %spin /control]~ this]
::
++  on-arvo
  |=  [=wire =sign-arvo]
  ?+  sign-arvo  (on-arvo:def wire sign-arvo)
      [%lick %soak *]
      ?+    mark.sign-arvo  [~ this]
        ::
          %connect
        ~&  >  "connect"
        :_  this
        :~  :*  %pass  /spit  %arvo  %l
                %spit  /control  %init  area.state
        ==  ==
      ==
  ==
::
++  send-state
  |=  =state
  ^-  card:agent:gall
  :*  %pass 
      /spit 
      %arvo %l 
      %spit 
      /control 
      %state 
      [slick:state face.state food.state live.state]
   ==
\end{lstlisting}

>>>>

%%MANUSCRIPT
\title{What\,Agreement\,Hath\,Mars\,With\,Earth? \\ An Exploration of Urbit's IPC Interfaces}
\author{~\authorpatp \\ \affiliation}
\date{}

@@

\begin{lstlisting}[
  float,
  style=listingcode,
  caption={Usage of \texttt{\%lick} cards.},
  label={lst:lick-cards}
]
++  init  [[%pass / %arvo %l %spin /control]~ this]
++  on-arvo
  |=  [=wire =sign-arvo]
  ?+    sign-arvo  (on-arvo:def wire sign-arvo)
      [%lick %soak *]
    ?+    mark.sign-arvo  [~ this]
        %connect
      :_  this
      :~  :*  %pass  /spit  %arvo  %l
              %spit  /control  %init  area.state
      ==  ==
  ==  ==
++  send-state
  |=  =state
  ^-  card:agent:gall
  :*  %pass  /spit  %arvo  %l 
      %spit  /control  %state
      [slick:state face.state food.state live.state]
  ==
\end{lstlisting}

@@
